Model Estimation

### 2018-12-07 model_estimation.Rmd
Revised how logsum gets into model estimation

  estimation_data <- tracts@data %>% 
    mutate(logsum = calculate_park_logsums(
      d = distances,  parks$log_size,
      betas = betas))

  sdm <- lagsarlm(update(model, . ~ . + logsum), data = estimation_data, 
                  listw = W, zero.policy = TRUE, type = "mixed")
  return(-as.numeric(logLik(sdm)))
}

@@

  estimation_data <- tracts@data %>% 
    mutate(logsum = calculate_park_logsums(
      distances,  parks$log_size,  parks$log_tweets,
      betas = betas))

  sdm <- lagsarlm(update(model, . ~ . + logsum), data = estimation_data, 
                  listw = W, zero.policy = TRUE, type = "mixed")

>>>>

  logsum <- calculate_park_logsums(
    d = distances,  sizes = parks$log_size,
    betas = betas)

  sdm <- lagsarlm(update(model, . ~ . + logsum), data = tracts@data, 
                  listw = W, zero.policy = TRUE, type = "mixed")
  return(-as.numeric(logLik(sdm)))
}

@@

  estimation_data <- tracts@data %>% 
    mutate(logsum = calculate_park_logsums(
      d = distances,  sizes = parks$log_size,  tweets = parks$log_tweets,
      betas = betas))

  sdm <- lagsarlm(update(model, . ~ . + logsum, data = tracts@data), 
                  listw = W, zero.policy = TRUE, type = "mixed")
